Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-09-12 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{SFig6.png}
    \caption{{\bf Buckling Optimization.} Graph shows optimal value of critical buckling strain for varying number of diagonals. For all simulations, the total mass of the structure is maintained constant while the mass-ratio is allowed to vary. Furthermore, the diagonal separation for each pair of diagonal is allowed to vary together ensuring half symmetry of the structure at all times. The optimization is run under a uni-axial loading condition.}
    \label{BucklingOptimization}
\end{figure}

@@

\mf{Write about minimum RVE}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{SFig6.png}
    \caption{{\bf Buckling Optimization.} Graph shows optimal value of critical buckling strain for varying number of diagonals. For all simulations, the total mass of the structure is maintained constant while the mass-ratio is allowed to vary. Furthermore, the diagonal separation for each pair of diagonal is allowed to vary together ensuring half symmetry of the structure at all times. The optimization is run under a uniaxial loading condition. The color of each point on the graph corresponds to the optimum value of mass ratio for that particular number of diagonals. Four deformation plots of the optimum structure and buckling modes are provided on the right for their respective number of diagonals.}
    \label{BucklingOptimization}
\end{figure}

@@

\mf{Write about minimum RVE -- how do I convey this message? Should I produce a plot or just verbally state this check?}
